Neural Neural Textures Make Sim2Real Consistent

### 2022-06-24 CORL/appendix.tex
Added algorithm comparison video

>>>>

		\begin{figure}[H]
			\begin{center}
			\href{https://youtu.be/-GSixT4shxY}{
					\includegraphics[width=400pt]{../images/algo_comparison_thumbnail.pdf}
					}
				\end{center}
			\caption{
				This animation shows an animation of various algorithms on a dataset with 5 alphabet blocks moving around. 
				When watching, note how the numbers on the top of the cubes in both CycleGAN and CUT change over time, while with TRITON they stay the same.
				Url: \href{https://youtu.be/-GSixT4shxY}{youtu.be/-GSixT4shxY}
			}
			\label{fig:algocomparisonvideo}
		\end{figure}
